---
title: "1/5 - Coursera Developing Data Products - Course Project Shiny Application and Reproducible Pitch"
author: "Stefano Valbonesi"
date: "2023-03-28"
output:
  slidy_presentation: default
  powerpoint_presentation: default
  ioslides_presentation: default
---

## 2/5 - Overview

> I must create a Shiny application and deploy it on Rstudio's servers.
It must include some form of input, operation on ui input on server.R, reactive output.
Then, I must create a reproducible pitch presentation (5 slides).

> Here is the link of my shiny application:
https://avvakum73.shinyapps.io/course_project/?_ga=2.40042018.1075172609.1680023325-138698224.1680023325

> Here is the link for the codes of server.R and ui.R:
https://github.com/AvvA73/Developing_Data_Product_Course_Project

## 3/5 - Description of my App

> In this shiny app you can calculate the HDL level of cholesterol
by inserting your levels of total cholesterol, LDL and trygliceride.
The computation is based of Friedwald formula.

## 4/5 - ui.R code

```{r, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Prediction for Diabetes"),
  sidebarLayout(
    sidebarPanel(
      numericInput(inputId="tcol",label="Total cholesterol (mg/dl)",value=80,min=30,max=1000,step=1),
      numericInput(inputId="ldl",label="LDL cholesterol (mg/dl)",value=80,min=30,max=1000,step=1),
      numericInput(inputId="trig",label="triglyceride (in mg/dl)",value=80,min=30,max=1000,step=1),
      submitButton("Submit")
    ),
    mainPanel(
      h2("Your results"),
      h3("HDL cholesterol"),
      textOutput("text1")
    )
    )
  ))
)
```

## 5/5 - server.R code

```{r, eval=FALSE}
library(shiny)
shinyServer(function(input,output) {
  output$text1<-renderText(input$tcol-(input$ldl+(input$trig/5)))
})
```
